Submission and Formatting Instructions for \\ International Conference on Machine Learning (ICML 2019)

### 2019-04-24 paper/icml_ai4good/main.tex
updated

\section{Introduction}
Ending the epidemics of AIDS, tuberculosis, malaria and other infectious diseases by 2030 is a key target by the Good Health & Well-Being section of the UN Sustainable Development Goals. Despite decades of substantial international efforts, malaria still annually kills about a quarter of a million children under the age of 5 in Africa alone.

@@

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
% \usepackage{graphicx}
% Please add the following required packages to your document preamble:
% \usepackage{graphicx}
%\begin{table*}[b!]
%\footnotesize
%\setlength{\tabcolsep}{1mm}
%\caption{Addresses}
%\label{table:addresses}
%\def\arraystretch{1.25}
%% \setlength{\tabcolsep}{1mm}
%\begin{tabularx}{\textwidth}{@{}lX@{}} 
%\toprule
%Address & Physical event                                                                                                                            \midrule
%1 & [forward()+0x204; OM::Simulator::start(scnXml::Monitoring const)+0x28a; OM::Population::createInitialHumans()+0x94; OM::Population::newHuman(OM::SimTime)+0x5c; OM::Host::Human::Human(OM::SimTime)+0x12b; OM::WithinHost::WHInterface::createWithinHostModel(double)+0x99; OM::WithinHost::DescriptiveWithinHostModel::DescriptiveWithinHostModel(double)+0x3a; OM::WithinHost::WHFalciparum::WHFalciparum(double)+0xe6; OM::util::random::gauss(double, double)+0xb4]\_\_Normal\\
%2 & [forward()+0x204; OM::Simulator::start(scnXml::Monitoring const\&)+0x468; OM::Population::update1(OM::SimTime)+0x1e9; OM::Population::newHuman(OM::SimTime)+0x5c; OM::Host::Human::Human(OM::SimTime)+0x12b; OM::WithinHost::WHInterface::createWithinHostModel(double)+0x99; OM::WithinHost::DescriptiveWithinHostModel::DescriptiveWithinHostModel(double)+0x3a; OM::WithinHost::WHFalciparum::WHFalciparum(double)+0xe6; OM::util::random::gauss(double, double)+0xb4]\_\_Normal\\
%3 & [forward()+0x204; OM::Simulator::start(scnXml::Monitoring const\&)+0x468; OM::Population::update1(OM::SimTime)+0xff; OM::Host::Human::update(bool)+0x22c; OM::Host::InfectionIncidenceModel::numNewInfections(OM::Host::Human const\&, double)+0x2a3; OM::util::random::poisson(double)+0x13f]\_\_Poisson\\
%4 & [forward()+0x204; OM::Simulator::start(scnXml::Monitoring const\&)+0x468; OM::Population::update1(OM::SimTime)+0xff; OM::Host::Human::update(bool)+0x2bc; OM::Clinical::ClinicalModel::update(OM::Host::Human\&, double, bool)+0x96; OM::Host::NeonatalMortality::eventNeonatalMortality()+0x9; OM::util::random::uniform\_01()+0xc0]\_\_Uniform\\
%5 & [forward()+0x204; OM::Simulator::start(scnXml::Monitoring const\&)+0x468; OM::Population::update1(OM::SimTime)+0xff; OM::Host::Human::update(bool)+0x2bc; OM::Clinical::ClinicalModel::update(OM::Host::Human\&, double, bool)+0x96; OM::Host::NeonatalMortality::eventNeonatalMortality()+0x9; OM::util::random::uniform\_01()+0xc0]\_\_Uniform\\
%6 & [forward()+0x204; OM::Simulator::start(scnXml::Monitoring const\&)+0x468; OM::Population::update1(OM::SimTime)+0xff; OM::Host::Human::update(bool)+0x280; OM::WithinHost::DescriptiveWithinHostModel::update(int, std::vector \textgreater{}\&, double, double)+0x3a2; OM::WithinHost::DescriptiveInfection::determineDensities(double, double, double, double\&, double, double)+0x303; OM::util::random::uniform\_01()+0xc0]\_\_Uniform\\
%7 & [forward()+0x204; OM::Simulator::start(scnXml::Monitoring const\&)+0x468; OM::Population::update1(OM::SimTime)+0xff; OM::Host::Human::update(bool)+0x2bc; OM::Clinical::ClinicalModel::update(OM::Host::Human\&, double, bool)+0xe8; OM::Clinical::CM5DayCommon::doClinicalUpdate(OM::Host::Human\&, double)+0x67; OM::WithinHost::WHFalciparum::determineMorbidity(OM::Host::Human\&, double, bool)+0x73; OM::WithinHost::Pathogenesis::PathogenesisModel::determineState(OM::Host::Human\&, double, double, double, bool)+0x143; OM::util::random::bernoulli(double)+0x47; OM::util::random::uniform\_01()+0xc0]\_\_Uniform\\
%8 & [forward()+0x204; OM::Simulator::start(scnXml::Monitoring const\&)+0x468; OM::Population::update1(OM::SimTime)+0xff; OM::Host::Human::update(bool)+0x2bc; OM::Clinical::ClinicalModel::update(OM::Host::Human\&, double, bool)+0xe8; OM::Clinical::CM5DayCommon::doClinicalUpdate(OM::Host::Human\&, double)+0x67; OM::WithinHost::WHFalciparum::determineMorbidity(OM::Host::Human\&, double, bool)+0x73; OM::WithinHost::Pathogenesis::PathogenesisModel::determineState(OM::Host::Human\&, double, double, double, bool)+0x162; OM::util::random::bernoulli(double)+0x47; OM::util::random::uniform\_01()+0xc0]\_\_Uniform\\
%9 & [forward()+0x204; OM::Simulator::start(scnXml::Monitoring const\&)+0x468; OM::Population::update1(OM::SimTime)+0xff; OM::Host::Human::update(bool)+0x2bc; OM::Clinical::ClinicalModel::update(OM::Host::Human\&, double, bool)+0xe8; OM::Clinical::CM5DayCommon::doClinicalUpdate(OM::Host::Human\&, double)+0x67; OM::WithinHost::WHFalciparum::determineMorbidity(OM::Host::Human\&, double, bool)+0x73; OM::WithinHost::Pathogenesis::PathogenesisModel::determineState(OM::Host::Human\&, double, double, double, bool)+0x1c7; OM::util::random::bernoulli(double)+0x47; OM::util::random::uniform\_01()+0xc0]\_\_Uniform\\
%10 & [forward()+0x204; OM::Simulator::start(scnXml::Monitoring const\&)+0x468; OM::Population::update1(OM::SimTime)+0xff; OM::Host::Human::update(bool)+0x2bc; OM::Clinical::ClinicalModel::update(OM::Host::Human\&, double, bool)+0xe8; OM::Clinical::CM5DayCommon::doClinicalUpdate(OM::Host::Human\&, double)+0xe3; OM::Clinical::ImmediateOutcomes::uncomplicatedEvent(OM::Host::Human\&, OM::Clinical::Episode::State)+0x87; OM::util::random::uniform\_01()+0xc0]\_\_Uniform\\
%11 & [forward()+0x204; OM::Simulator::start(scnXml::Monitoring const\&)+0x468; OM::Population::update1(OM::SimTime)+0xff; OM::Host::Human::update(bool)+0x2bc; OM::Clinical::ClinicalModel::update(OM::Host::Human\&, double, bool)+0xe8; OM::Clinical::CM5DayCommon::doClinicalUpdate(OM::Host::Human\&, double)+0xad; OM::Clinical::CM5DayCommon::severeMalaria(OM::Host::Human\&, OM::Clinical::Episode::State, double, int\&)+0x4b1; OM::util::random::uniform\_01()+0xc0]\_\_Uniform\\
%\bottomrule                                                                                                                                   
%\end{tabularx}
% \end{table*}
% \subsubsection*{Acknowledgments}

% Use unnumbered third level headings for the acknowledgments. All acknowledgments
% go at the end of the paper. Do not include acknowledgments in the anonymized
% submission, only in the final paper.

\section*{References}

>>>>

\section{Introduction}
Ending the epidemics of AIDS, tuberculosis, malaria and other infectious diseases by 2030 is a key target by the Good Health \& Well-Being section of the UN Sustainable Development Goals. Despite decades of substantial international efforts, malaria still annually kills about a quarter of a million children under the age of 5 in Africa alone.

@@

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
% \usepackage{graphicx}
% Please add the following required packages to your document preamble:
% 
% \begin{table*}[b!]
% \footnotesize
% \setlength{\tabcolsep}{1mm}
% \caption{Addresses}
% \label{table:addresses}
% \def\arraystretch{1.25}
% % \setlength{\tabcolsep}{1mm}
% \begin{tabularx}{\textwidth}{@{}lX@{}} 
% \toprule
% Address & Physical event                                                                                                                            \midrule
%
% 
% 
% \bottomrule                                                                                                                                   
% \end{tabularx}
% \end{table*}

  \begin{table*}[b!]
  \footnotesize
  \setlength{\tabcolsep}{1mm}
  \caption{Addresses }
  \label{table:addresses}
  \def\arraystretch{1.25}
  % \setlength{\tabcolsep}{1mm}
  \begin{tabularx}{\textwidth}{@{}lX@{}} 
    \toprule
    Address ID & Full address \\
    \midrule
  A1 & [forward()+0x204; OM::Simulator::start(scnXml::Monitoring const)+0x28a;

  OM::Population::createInitialHumans()+0x94;

  OM::Population::newHuman(OM::SimTime)+0x5c;

  OM::Host::Human::Human(OM::SimTime)+0x12b;

  OM::WithinHost::WHInterface::createWithinHostModel(double)+0x99;

  OM::WithinHost::DescriptiveWithinHostModel::DescriptiveWithinHostModel(double)+0x3a;

  OM::WithinHost::WHFalciparum::WHFalciparum(double)+0xe6;

  OM::util::random::gauss(double, double)+0xb4]\_\_Normal\\
  A2 & [forward()+0x204; 
  OM::Simulator::start(scnXml::Monitoring const\&)+0x468;

   OM::Population::update1(OM::SimTime)+0x1e9;

   OM::Population::newHuman(OM::SimTime)+0x5c;

   OM::Host::Human::Human(OM::SimTime)+0x12b;

   OM::WithinHost::WHInterface::createWithinHostModel(double)+0x99;

   OM::WithinHost::DescriptiveWithinHostModel::DescriptiveWithinHostModel(double)+0x3a;

   OM::WithinHost::WHFalciparum::WHFalciparum(double)+0xe6;

   OM::util::random::gauss(double, double)+0xb4]\_\_Normal \\
  A3 & [forward()+0x204; OM::Simulator::start(scnXml::Monitoring const\&)+0x468;

   OM::Population::update1(OM::SimTime)+0xff;

   OM::Host::Human::update(bool)+0x22c;

   OM::Host::InfectionIncidenceModel::numNewInfections(OM::Host::Human const\&, double)+0x2a3;

   OM::util::random::poisson(double)+0x13f]\_\_Poisson\\
  A4 & [forward()+0x204; OM::Simulator::start(scnXml::Monitoring const\&)+0x468;

  OM::Population::update1(OM::SimTime)+0xff; OM::Host::Human::update(bool)+0x2bc;

   OM::Clinical::ClinicalModel::update(OM::Host::Human\&, double, bool)+0x96;

   OM::Host::NeonatalMortality::eventNeonatalMortality()+0x9;

    OM::util::random::uniform\_01()+0xc0]\_\_Uniform\\
  A5 & [forward()+0x204; OM::Simulator::start(scnXml::Monitoring const\&)+0x468;

   OM::Population::update1(OM::SimTime)+0xff;

    OM::Host::Human::update(bool)+0x2bc;

    OM::Clinical::ClinicalModel::update(OM::Host::Human\&, double, bool)+0x96;

    OM::Host::NeonatalMortality::eventNeonatalMortality()+0x9;

    OM::util::random::uniform\_01()+0xc0]\_\_Uniform\\
  A6 & [forward()+0x204; OM::Simulator::start(scnXml::Monitoring const\&)+0x468;

   OM::Population::update1(OM::SimTime)+0xff;

   OM::Host::Human::update(bool)+0x280;

   OM::WithinHost::DescriptiveWithinHostModel::update(int, std::vector \textgreater{}\&, double, double)+0x3a2;

   OM::WithinHost::DescriptiveInfection::determineDensities(double, double, double, double\&, double, double)+0x303;

   OM::util::random::uniform\_01()+0xc0]\_\_Uniform\\
   A7 & [forward()+0x204; OM::Simulator::start(scnXml::Monitoring const\&)+0x468;
   ı
	OM::Population::update1(OM::SimTime)+0xff;

	OM::Host::Human::update(bool)+0x2bc;

	OM::Clinical::ClinicalModel::update(OM::Host::Human\&, double, bool)+0xe8;

	OM::Clinical::CM5DayCommon::doClinicalUpdate(OM::Host::Human\&, double)+0x67;

	OM::WithinHost::WHFalciparum::determineMorbidity(OM::Host::Human\&, double, bool)+0x73;
ı
	OM::WithinHost::Pathogenesis::PathogenesisModel::determineState(OM::Host::Human\&, double, double, double, bool)+0x143;

	OM::util::random::bernoulli(double)+0x47;

	OM::util::random::uniform\_01()+0xc0]\_\_Uniform\\
	A8 & [forward()+0x204; OM::Simulator::start(scnXml::Monitoring const\&)+0x468;

	OM::Population::update1(OM::SimTime)+0xff; OM::Host::Human::update(bool)+0x2bc;

	OM::Clinical::ClinicalModel::update(OM::Host::Human\&, double, bool)+0xe8;

	OM::Clinical::CM5DayCommon::doClinicalUpdate(OM::Host::Human\&, double)+0x67;

	OM::WithinHost::WHFalciparum::determineMorbidity(OM::Host::Human\&, double, bool)+0x73;

	OM::WithinHost::Pathogenesis::PathogenesisModel::determineState(OM::Host::Human\&, double, double, double, bool)+0x162;

	OM::util::random::bernoulli(double)+0x47;

	OM::util::random::uniform\_01()+0xc0]\_\_Uniform\\
A9 & [forward()+0x204; OM::Simulator::start(scnXml::Monitoring const\&)+0x468;
 OM::Population::update1(OM::SimTime)+0xff; OM::Host::Human::update(bool)+0x2bc;

 OM::Clinical::ClinicalModel::update(OM::Host::Human\&, double, bool)+0xe8;

  OM::Clinical::CM5DayCommon::doClinicalUpdate(OM::Host::Human\&, double)+0x67;

  OM::WithinHost::WHFalciparum::determineMorbidity(OM::Host::Human\&, double, bool)+0x73;

  OM::WithinHost::Pathogenesis::PathogenesisModel::determineState(OM::Host::Human\&, double, double, double, bool)+0x1c7;

  OM::util::random::bernoulli(double)+0x47; OM::util::random::uniform\_01()+0xc0]\_\_Uniform\\
\bottomrule
  \end{tabularx}
  \end{table*}
% \subsubsection*{Acknowledgments}

% Use unnumbered third level headings for the acknowledgments. All acknowledgments
% go at the end of the paper. Do not include acknowledgments in the anonymized
% submission, only in the final paper.
  \begin{table*}[ht!]
  \footnotesize
  \setlength{\tabcolsep}{1mm}
  \caption{Addresses .}
  \label{table:addresses}
  \def\arraystretch{1.25}
  % \setlength{\tabcolsep}{1mm}
  \begin{tabularx}{\textwidth}{@{}lX@{}} 
    \toprule
    Address ID & Full address \\
    \midrule
A10 & [forward()+0x204; OM::Simulator::start(scnXml::Monitoring const\&)+0x468;

OM::Population::update1(OM::SimTime)+0xff; OM::Host::Human::update(bool)+0x2bc;

OM::Clinical::ClinicalModel::update(OM::Host::Human\&, double, bool)+0xe8;

OM::Clinical::CM5DayCommon::doClinicalUpdate(OM::Host::Human\&, double)+0xe3;

OM::Clinical::ImmediateOutcomes::uncomplicatedEvent(OM::Host::Human\&, OM::Clinical::Episode::State)+0x87;

OM::util::random::uniform\_01()+0xc0]\_\_Uniform\\
A11 & [forward()+0x204; OM::Simulator::start(scnXml::Monitoring const\&)+0x468;
OM::Population::update1(OM::SimTime)+0xff; OM::Host::Human::update(bool)+0x2bc;

OM::Clinical::ClinicalModel::update(OM::Host::Human\&, double, bool)+0xe8;

OM::Clinical::CM5DayCommon::doClinicalUpdate(OM::Host::Human\&, double)+0xad;

OM::Clinical::CM5DayCommon::severeMalaria(OM::Host::Human\&, OM::Clinical::Episode::State, double, int\&)+0x4b1;
OM::util::random::uniform\_01()+0xc0]\_\_Uniform\\
    \bottomrule
  \end{tabularx}
  \end{table*}
\section*{References}
